---
title: "Climate Change Midpoint"
author: "Pranav Vasan, Arnav Gupta, Prerna Sheokand, Emily Giverts, Datta Dave"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
library("knitr")
source("scripts/chart1.R")
source("scripts/chart2.R")
library("dplyr")
library("ggplot2")
library("tidyr")
library("lintr")
lint("scripts/chart1.R")
lint("scripts/chart2.R")
```

```{r dataset, echo=FALSE}
emission_data <- read.csv(file = "data/fossil-fuel-co2-emissions-by-nation.csv",
                          stringsAsFactors = FALSE)
```


## Introduction

Climate change has been a popular and important topic of discussion amongst people for several years now. Numerous scientists have gathered vast amounts of data to dicover trends in climate change over the decades. This project attempts to gather data from the last several centuries regarding fossil fuel carbon dioxide emission. This is very important, especially in the current day, because it will allow people to understand the effect of climate change and start taking preventive measures. Our [dataset](https://datahub.io/core/co2-fossil-by-nation) contains data from the Carbon Dioxide Information Analysis Center (CDIAC) for numerous countries from 1751 to 2014.

## Summary Information



## Summary Table



## Chart 1

```{r line_graph, echo=FALSE}
line_graph(emission_data)
```



## Chart 2

```{r bar_chart, echo=FALSE}
bar_graph(emission_data)
```
- The purpose of this chart was to look at a breakdown of each carbon emitting source in relation to the total for the top 10 carbon emitting countries in the most recent year available (2014). 
- In 2014, cement was relatively the smallest carbon source used in each of the 10 countries.
- In 2014, China and India used a majority of solid fuel relative to all carbon emission sources.
- Saudi Arabia and the Islamic Republic of Iran used no solid fuel in 2014.
- Gas Flaring was only used in the Islamic Republic of Iran and the Russian Federation.


## Chart 3


